\Large Generative Dynamics of Supreme Court Citations: \\ Analysis with a New Statistical Model

### 2020-08-25 Tex/PA_rrmemo/PA_RnR_memo.tex
Added and updated appendix
updated memo to reflect expanded results in paper

\noindent \textbf{Addressed:} All networks were estimated using MCMLE, however, for smaller networks we used the network's MPLE as the algorithms's starting value, while for larger networks the starting value was obtained using simulated annealing, since the MPLE as starting value did not lead to converged MCMLEs anymore. While in theory the algorithm should converge to the MLE regardless of the starting value, in practice this is not the case   \cite{hummel2012improving}. \\
In order to be consistent with the used estimation approach, we estimate the MCMLE now for all networks using simulated annealing starting value. The results have not changed noticeably.  \\

@@

\noindent \textbf{R1.3:} \emph{ Relatedly, why isn’t overtime change in the covariates discussed? The authors instead choose to make broad statements: “in/consistently significant” over the period of study.  This seems to be a wasted opportunity and contrary to their motivation (a la Shalizi and Rinaldo 2013). If the authors want to make a statement about whether the covariate generally holds, then why not run a single model across all the years? Otherwise, wouldn’t it make sense to discuss these over time changes, at least when they appear to be quite meaningful?  }\\

@@

\noindent \textbf{R1.4:} \emph{ Not to belabor the point, but the motivation for the exogenous and endogenous terms are nicely situated in the literature, but the discussion of the results are quite anticlimactic. It merely notes that some results are generally in line with expectations while others are not (the ideology finding being terribly interesting and surprising!). I’d like to see a more substantive engagement with the results, particularly any trends / disruptions in the series of coefficients. This has the potential to be a much bigger contribution to the judicial literature than the authors acknowledge.  }\\

\noindent \textbf{R1.5:} \emph{ While this is a well-executed paper (and visually beautiful), it’s not clear where the contribution is meant to be. Is this paper an introduction of a new model or an application of the ERGM to citation data?  If this is a new network model that would merit its own name, c-ERGM, what other networks might this model apply to?  Does it really make sense to have a model that just applies to this one judicial network...? I suppose this model works for any citations --- e.g., academic papers -- so maybe discussing a bit of that literature and data would help. In short, the change to the ERGM is slight, even when combining that with the necessary simulated estimation approach, so telling us why these changes are so useful beyond this network could drive home the methodological contribution.  }\\

\noindent \textbf{R1.6:} \emph{ Alternatively, one could think about this paper more in terms of its substantive contributions. The front end is deeply ingrained in the citations and judicial literatures, as are the data, of course, but little attention is given in the end to what we learn from this paper. It seems like the authors decided not to engage either frame fully, which leaves the contribution lacking on both. Having said that, I think one could go either way with this paper, and I liked a lot about it on both fronts. }\\

>>>>

\noindent \textbf{Addressed:} All networks were estimated using MCMLE, however, for smaller networks we used the network's MPLE as the algorithms's starting value, while for larger networks the starting value was obtained using simulated annealing, since the MPLE as starting value did not lead to converged MCMLEs anymore. While in theory the algorithm should converge to the MLE regardless of the starting value, in practice this is not the case   \cite{hummel2012improving}. \\
In order to be consistent with the used estimation approach, we estimate the MCMLE now for all networks using simulated annealing starting value. The results have not changed noticeably.  \\
The text in the appendix has been updated accordingly.\\

@@

\noindent \textbf{R1.3:} \emph{ Relatedly, why isn’t overtime change in the covariates discussed? The authors instead choose to make broad statements: “in/consistently significant” over the period of study.  This seems to be a wasted opportunity and contrary to their motivation (a la Shalizi and Rinaldo 2013). If the authors want to make a statement about whether the covariate generally holds, then why not run a single model across all the years? Otherwise, wouldn’t it make sense to discuss these over time changes, at least when they appear to be quite meaningful? Not to belabor the point, but the motivation for the exogenous and endogenous terms are nicely situated in the literature, but the discussion of the results are quite anticlimactic. It merely notes that some results are generally in line with expectations while others are not (the ideology finding being terribly interesting and surprising!). I’d like to see a more substantive engagement with the results, particularly any trends / disruptions in the series of coefficients. This has the potential to be a much bigger contribution to the judicial literature than the authors acknowledge. }\\

\noindent \textbf{Addressed:} We thank the reviewer for pushing us to expand on our results; we believe the extended discussion greatly improves the paper. We changed the results section in two main ways (pp. 13-14).

First, we situated our more unexpected findings (i.e. negative outdegree count and ideological distance) in the courts and legal studies literatures. For these findings, we offer explanations that comport with the field's understanding of justice behavior. The hub effect is negative because outdegree count reflects case complexity, and justices avoid citing these opinions in anticipation of them being overruled. Judges are more likely to cite ideologically distant cases because they increasingly attempt to provide more balanced opinions.

Second, we extend this discussion to account for temporal dynamics. Using these same effects, we illustrate how our approach of fitting term-by-term models allows us to better capture the complexities that arise from both the temporal context (e.g. chief justice characteristics) and from the network growth characteristic of citation networks.\\

\noindent \textbf{R1.4:} \emph{ While this is a well-executed paper (and visually beautiful), it’s not clear where the contribution is meant to be. Is this paper an introduction of a new model or an application of the ERGM to citation data?  If this is a new network model that would merit its own name, c-ERGM, what other networks might this model apply to?  Does it really make sense to have a model that just applies to this one judicial network...? I suppose this model works for any citations --- e.g., academic papers -- so maybe discussing a bit of that literature and data would help. In short, the change to the ERGM is slight, even when combining that with the necessary simulated estimation approach, so telling us why these changes are so useful beyond this network could drive home the methodological contribution.  }\\

@@

\noindent \textbf{R1.5:} \emph{ Alternatively, one could think about this paper more in terms of its substantive contributions. The front end is deeply ingrained in the citations and judicial literatures, as are the data, of course, but little attention is given in the end to what we learn from this paper. It seems like the authors decided not to engage either frame fully, which leaves the contribution lacking on both. Having said that, I think one could go either way with this paper, and I liked a lot about it on both fronts. }\\
